Improved Bounds for Online Balanced Repartitioning

### 2020-04-30 paper/disc20clustering.tex
Readability

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	Alg collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before Alg resets the counter.
	I.e.,
	$ C^t_{\set{u,v}} = \lambda$.
%	In case the first collocation of $\set{u,v}$ occurs at $t$,
%	if the pair is collocated in the initial configuration then
%	we set $t''=0$,
%	else,
%	we set $ t'' = -\infty, t'=0$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $(t_1,t_2]$ by $\sigma_{\set{x,y}}(t_1,t_2]$.
	If $t$ is the first time that Alg collocates $\{u,v\}$ then we  charge
	OPT $\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	 or $\alpha$ for collocating the pair and serving them with no additional cost.
	Therefore in this case ,
	OPT pays $\min{\{ \lambda,\alpha \}}$.
	Else,
	let $t'$, $t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some (intersecting) pair
	$\{x,y\} \neq \{u,v\}, \{x,y\} \cap \{u,v\} \neq \emptyset$, 
	e.g.,
	$\{x,y\}=\{u,v'\}$.
%	I.e., $ C^{t'}_{\set{u,v'}} = \lambda$.
	Similarly,
	if $t'$ is not the first time that Alg  collocates $\{u,v'\}$ 
	then let $t''<t'$ be the last time before $t'$ when Alg separates $\set{u,v'}$.
	Else,
	$\{u,v'\}$ is not collocated in the initial configuration and we let $t''=0$.
	By these definitions,
	we have
	$| \sigma_{\set{u,v'}}(t'',t'] | = | \sigma_{\set{u,v}}(t',t] |  =  \lambda$.
	The overall cost of requests in $\sigma_{\set{u,v}}(t',t]$,
	and the moving cost,
	incurred by Alg is
	$\lambda + 2\alpha$.
	Observe that for requests in $r_t := \sigma_{\{u,v'\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t]$,
	OPT must pay a total cost of serving and (or) migration at least
	$\min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$
	within $(0,m]$,
	regardless of its choices.
	%% 
	However,
	we cannot charge this cost to OPT repeatedly,
	i.e.,
	when Alg collocates the two pairs a second time.
	In particular,
	we charge OPT a cost incurred by requests in
	$\sigma_{\{u,v'\}}(t'',t']$ and $\sigma_{\{u,v\}}(t',t]$,
	if and only if  OPT incurs the cost within  intervals $(t'', t']$ and $(t', t]$,
	respectively.	
	Latter,
	this ensures us that we do not charge OPT for a cost more than twice.
	%%
	Based on this observation,
	we distinguish three cases of OPT's choices
	while it serves requests in	$r_t $.
	We denote its cost by
	$\mathit{Cost}_{\mathit{OPT}} (r_t) := \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v'\}}(t'',t']) 
	+ \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}(t',t]) $.
	\begin{enumerate}[label=\roman*.]
		\item
		OPT collocates $\{u,v'\}$ at  $t''$, $\{u,v\}$  at $t'$,
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $r_t$ with no additional cost and
		$\mathit{Cost}_{\mathit{OPT}} (r_t) = 2\alpha$.
		\item
		OPT has $\{u,v\}$ ($\{u,v'\}$) already collocated at $t'$ ($t''$) as well as during $(t',t]$ ($(t'',t]$),
		and has $\{u,v'\}$ ($\{u,v\}$) separated during $(t'',t']$ ($(t',t]$).
		Hence,
		it pays only $\lambda$ for serving all requests in $r_t$ and
		$\mathit{Cost}_{\mathit{OPT}} (r_t) = \lambda$
		\item
		OPT has $\{u,v'\}$ ($\{u,v\}$) already  collocated at $t''$ ($t'$)  and also during $(t'',t']$ ($(t', t])$,
		 and it collocates $\{u,v\}$ ($\{u,v'\}$) at $t'+1$ ($t''+1$) paying $\alpha$.
%		Therefore it pays only $\alpha$ during $[t'',t]$,
%		for collocating $\{u,v'\}$
%	    and for the one request to $\{u,v\}$ at $t'$.
%		I.e., it pays zero for every other  request in $r_t$.
Then,
$\mathit{Cost}_{\mathit{OPT}} (r_t) = \alpha$.
	 In every of these cases,
   	we have
   	$\mathit{Cost}_{\mathit{OPT}} (r_t) \geq  \min{ \{ \lambda, \alpha \}}$.
  	OPT may deviate from these cases,
	e.g.~by collocating a pair after partially paying for requests to this pair.
	 However,
	 no deviation can decrease the cost to OPT.
	 \mahmoud{It would be better to describe and bound the "deviation" formally.}
	Therefore in any case,
 	$\mathit{Cost}_{\mathit{OPT}} (r_t) \geq  \min{ \{ \lambda, \alpha \}}$.

>>>>

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	Alg collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before Alg resets the counter.
	I.e.,
	$ C^t_{\set{u,v}} = \lambda$.
%	In case the first collocation of $\set{u,v}$ occurs at $t$,
%	if the pair is collocated in the initial configuration then
%	we set $t''=0$,
%	else,
%	we set $ t'' = -\infty, t'=0$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $(t_1,t_2]$ by $\sigma_{\set{x,y}}(t_1,t_2]$.

	If $t$ is the first time that Alg collocates $\{u,v\}$ then we  charge
	OPT $\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	 or $\alpha$ for collocating the pair and serving them with no additional cost.
	Therefore in this case ,
	OPT pays $\min{\{ \lambda,\alpha \}}$.

	In the remainder of this proof, we consider that Alg collocated $\{u,v\}$ in the past.
	Let $t'$, $t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some (intersecting) pair
	$\{x,y\} \neq \{u,v\}, \{x,y\} \cap \{u,v\} \neq \emptyset$, 
	e.g.,
	$\{x,y\}=\{u,v'\}$.
%	I.e., $ C^{t'}_{\set{u,v'}} = \lambda$.
	Similarly,
	if $t'$ is not the first time that Alg  collocates $\{u,v'\}$ 
	then let $t''<t'$ be the last time before $t'$ when Alg separates $\set{u,v'}$.
	Else,
	$\{u,v'\}$ is not collocated in the initial configuration and we let $t''=0$.
	By these definitions,
	we have
	$| \sigma_{\set{u,v'}}(t'',t'] | = | \sigma_{\set{u,v}}(t',t] |  =  \lambda$.
	The overall cost of requests in $\sigma_{\set{u,v}}(t',t]$,
	and the moving cost,
	incurred by Alg is
	$\lambda + 2\alpha$.
	Observe that for requests in $r_t := \sigma_{\{u,v'\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t]$,
	OPT must pay a total cost of serving and (or) migration at least
	$\min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$
	within $(0,m]$,
	regardless of its choices.
	%% 
	However,
	we cannot charge this cost to OPT repeatedly,
	i.e.,
	when Alg collocates the two pairs a second time.
	In particular,
	we charge OPT a cost incurred by requests in
	$\sigma_{\{u,v'\}}(t'',t']$ and $\sigma_{\{u,v\}}(t',t]$,
	if and only if  OPT incurs the cost within  intervals $(t'', t']$ and $(t', t]$,
	respectively.	
	Latter,
	this ensures us that we do not charge OPT for a cost more than twice.
	%%
	Based on this observation,
	we distinguish three cases of OPT's choices
	while it serves requests in	$r_t $.
	We denote its cost by
	$\mathit{Cost}_{\mathit{OPT}} (r_t) := \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v'\}}(t'',t']) 
	+ \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}(t',t]) $.
	\begin{enumerate}[label=\roman*.]
		\item
		OPT collocates $\{u,v'\}$ at  $t''$, $\{u,v\}$  at $t'$,
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $r_t$ with no additional cost and
		$\mathit{Cost}_{\mathit{OPT}} (r_t) = 2\alpha$.
		\item
		OPT has $\{u,v\}$ ($\{u,v'\}$) already collocated at $t'$ ($t''$) as well as during $(t',t]$ ($(t'',t]$),
		and has $\{u,v'\}$ ($\{u,v\}$) separated during $(t'',t']$ ($(t',t]$).
		Hence,
		it pays only $\lambda$ for serving all requests in $r_t$ and
		$\mathit{Cost}_{\mathit{OPT}} (r_t) = \lambda$
		\item
		OPT has $\{u,v'\}$ ($\{u,v\}$) already  collocated at $t''$ ($t'$)  and also during $(t'',t']$ ($(t', t])$,
		 and it collocates $\{u,v\}$ ($\{u,v'\}$) at $t'+1$ ($t''+1$) paying $\alpha$.
%		Therefore it pays only $\alpha$ during $[t'',t]$,
%		for collocating $\{u,v'\}$
%	    and for the one request to $\{u,v\}$ at $t'$.
%		I.e., it pays zero for every other  request in $r_t$.
Then,
$\mathit{Cost}_{\mathit{OPT}} (r_t) = \alpha$.
	\end{enumerate}
	 In every of these cases,
   	we have
   	$\mathit{Cost}_{\mathit{OPT}} (r_t) \geq  \min{ \{ \lambda, \alpha \}}$.
  	OPT may deviate from these cases,
	e.g.~by collocating a pair after partially paying for requests to this pair.
	 However,
	 no deviation can decrease the cost to OPT.
	 \mahmoud{It would be better to describe and bound the "deviation" formally.}
	Therefore in any case,
 	$\mathit{Cost}_{\mathit{OPT}} (r_t) \geq  \min{ \{ \lambda, \alpha \}}$.
